Lessons learned from bugs in models of human history

### 2020-08-03 paper.tex
figure and caption updates

\section*{Methods}

@@

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/ooa_expected_stats.pdf}}
\caption{\textbf{Expected diversity statistics under the \citet{gutenkunst2009inferring} model}.
    \textbf{(A)} The correctly implemented model. Dashed arrows depict continuous migration.
    \textbf{(B)} The incorrectly implemented model from the \msprime\ tutorial, with migration continuing
    into the past beyond the mass migration event with proportion $1$ from the ancestral population
    to the bottleneck population.
    \textbf{(C)} Marginal allele frequency spectra under the two models. Heterozygosity in the incorrect model
    is inflated by $\sim3.5\%$, though the general shape of the distributions are qualitatively similar.
    \textbf{(D)} Similarly, the increased heterozygosity leads to excess $D^2$, though the LD-decay is
    qualitatively similar between models.
    \textbf{(E-G)} True size history for each population plotted against the expected size history computed
    from the inverse coalescence rates under each model.
}
\label{fig:ooa_stats}
\end{center}
\end{figure}

>>>>

\section*{Data and Code Availability}

@@

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/ooa_expected_stats.pdf}}
\caption{\textbf{Expected diversity statistics under the \citet{gutenkunst2009inferring} model}.
    \textbf{(A)} The correctly implemented model. Dashed arrows depict continuous migration.
    \textbf{(B)} The incorrectly implemented model from the \msprime\ tutorial, with migration continuing
    into the past beyond the mass migration event with proportion $1$ from the ancestral population
    to the bottleneck population.
    \textbf{(C)} Marginal allele frequency spectra under the two models. Heterozygosity in the incorrect model
    is inflated by $\sim3.5\%$, though the general shape of the distributions are qualitatively similar.
    \textbf{(D)} Similarly, the increased heterozygosity leads to excess $D^2$, though the LD-decay is
    qualitatively similar between models.
    \textbf{(E-G)} We compared the true size history for each population under this model to their
    expected inverse coalescent rates, which are often interpreted as $N_e$. The correct and incorrect
    models (A and B) are equivalent in the recent history, so the inverse coalescence rates only differ
    in the more distant past. For multi-population demographic history, the inverse coalescence rates
    are not expected to match the ``true'' historical size along each branch, as population structure and
    migration between populations change coalescent probabilities over time.
}
\label{fig:ooa_stats}
\end{center}
\end{figure}
